R tools for accessing research literature for text mining

### 2019-08-23 manuscript.Rmd
fix #11 clarify the various crossref clients

The main interfaces for Crossref in R are [rcrossref][] and [crminer][]. Similar interfaces
are available in Ruby ([serrano][]) and Python ([habanero][]).

>>>>

The main interfaces for Crossref in R are [rcrossref][] and [crminer][]. rcrossref is a
complete client for the public facing Crossref web services including metadata, whereas crminer
focuses only on retrieving full text of articles. Similar interfaces to rcrossref
are available in Ruby ([serrano][]) and Python ([habanero][]).

### 2019-08-23 manuscript.tex
fix #11 clarify the various crossref clients

\hypertarget{crossrefdatacite}{%
\subsection{Crossref/Datacite}\label{crossrefdatacite}}

@@

The main interfaces for Crossref in R are
\href{https://github.com/ropensci/rcrossref}{rcrossref} and
\href{https://github.com/ropensci/crminer}{crminer}. Similar interfaces
are available in Ruby
(\href{https://github.com/sckott/serrano}{serrano}) and Python
(\href{https://github.com/sckott/habanero}{habanero}).

>>>>

\hypertarget{crossref-and-datacite}{%
\subsection{Crossref and Datacite}\label{crossref-and-datacite}}

@@

The main interfaces for Crossref in R are
\href{https://github.com/ropensci/rcrossref}{rcrossref} and
\href{https://github.com/ropensci/crminer}{crminer}. rcrossref is a
complete client for the public facing Crossref web services including
metadata, whereas crminer focuses only on retrieving full text of
articles. Similar interfaces to rcrossref are available in Ruby
(\href{https://github.com/sckott/serrano}{serrano}) and Python
(\href{https://github.com/sckott/habanero}{habanero}).
